Supplemental Online Materials:\\\textit{Double Standards in Judging Collective Action}

### 2024-11-05 Documents/supplemental-materials.qmd
2nd revision

We measured moral concerns with the 36-item moral foundations questionnaire [MFQ-2, @atari_morality_2022] which assesses to what extent participants endorse concerns about care, equality, proportionality, loyalty, authority, and purity (e.g., "I believe chastity is an important virtue."; 1 = *does not describe me at all*, 5 = *describes me extremely well*). We embedded three further attention checks within the questionnaire (e.g., "To show that you are paying attention and giving your best effort, please select 'moderately describes me'.").

@@

# References

>>>>

We measured moral concerns with the 36-item moral foundations questionnaire [MFQ-2, @atari_morality_2023] which assesses to what extent participants endorse concerns about care, equality, proportionality, loyalty, authority, and purity (e.g., "I believe chastity is an important virtue."; 1 = *does not describe me at all*, 5 = *describes me extremely well*). We embedded three further attention checks within the questionnaire (e.g., "To show that you are paying attention and giving your best effort, please select 'moderately describes me'.").

@@

\section*{References}

### 2024-11-05 Documents/supplemental-materials.tex
2nd revision

% Format
\usepackage[letterpaper, margin = 1in]{geometry}
\setcounter{secnumdepth}{0}
\usepackage{titlesec}  
\titleformat*{\section}{\centering\normalfont\Large\bfseries}

@@

We measured moral concerns with the 36-item moral foundations
questionnaire (MFQ-2, Atari et al., 2022) which assesses to what extent
participants endorse concerns about care, equality, proportionality,
loyalty, authority, and purity (e.g., ``I believe chastity is an
important virtue.''; 1 = \emph{does not describe me at all}, 5 =
\emph{describes me extremely well}). We embedded three further attention
checks within the questionnaire (e.g., ``To show that you are paying
attention and giving your best effort, please select `moderately
describes me'.'').

@@

\hypertarget{references}{%
\section{References}\label{references}}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-atari_morality_2022}{}}%
Atari, M., Haidt, J., Graham, J., Koleva, S., Stevens, S. T., \&
Dehghani, M. (2022). Morality beyond the {WEIRD}: How the nomological
network of morality varies across cultures. \emph{PsyArXiv}.
\url{https://doi.org/10.31234/osf.io/q6c9r}

>>>>

% Format
\usepackage[letterpaper, margin = 1in]{geometry}
\setcounter{secnumdepth}{2}
\renewcommand{\thesection}{\Alph{section}} 
\usepackage{titlesec}  
\titleformat*{\section}{\centering\normalfont\Large\bfseries}

@@

We measured moral concerns with the 36-item moral foundations
questionnaire (MFQ-2, Atari et al., 2023) which assesses to what extent
participants endorse concerns about care, equality, proportionality,
loyalty, authority, and purity (e.g., ``I believe chastity is an
important virtue.''; 1 = \emph{does not describe me at all}, 5 =
\emph{describes me extremely well}). We embedded three further attention
checks within the questionnaire (e.g., ``To show that you are paying
attention and giving your best effort, please select `moderately
describes me'.'').

@@

\section*{References}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-atari_morality_2023}{}}%
Atari, M., Haidt, J., Graham, J., Koleva, S., Stevens, S. T., \&
Dehghani, M. (2023). Morality beyond the {WEIRD}: {How} the nomological
network of morality varies across cultures. \emph{Journal of Personality
and Social Psychology}, \emph{125}(5), 1157--1188.
\url{https://doi.org/10.1037/pspp0000470}
